---
title: "Report"
format: html
---

# Use of antibiotics commonly associated with antimicrobial resistance

```{r get data, echo=FALSE, message = FALSE, warning = FALSE}
resultList <- list(
  "summarise_omop_snapshot",
  "summarise_observation_period",
  "summarise_cohort_count",
  "cohort_code_use",
  "summarise_cohort_attrition",
  "summarise_characteristics",
  "summarise_large_scale_characteristics",
  "incidence",
  "incidence_attrition",
  "summarise_drug_utilisation"
)

source(file.path(getwd(), "functions.R"))

data_path <- file.path(getwd(), "data")
csv_files <- list.files(data_path, pattern = "\\.csv$", full.names = TRUE)

result <- purrr::map(csv_files, \(x){
  d <- omopgenerics::importSummarisedResult(x)  
  d
}) |> 
  omopgenerics::bind() |>
  omopgenerics::newSummarisedResult()

resultList <- resultList |>
  purrr::map(\(x) {
    omopgenerics::settings(result) |>
      dplyr::filter(.data$result_type %in% .env$x) |>
      dplyr::pull(.data$result_id) }) |>
  rlang::set_names(resultList)

data <- prepareResult(result, resultList)
```

## Table 1 - Database descriptions

```{r db desc, echo=FALSE, message = FALSE, warning = FALSE}
snap <- data[["summarise_omop_snapshot"]] |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ))

OmopSketch::tableOmopSnapshot(snap, type = "flextable")
```

## Table 2 - Ciprofloxacin patient characteristics + indications

```{r char cipro, echo=FALSE, message = FALSE, warning = FALSE}
char <- data[["summarise_characteristics"]] |>
  dplyr::filter(group_level == "2551_ciprofloxacin",
                !variable_name %in% c("Antibiotics (-90 to -15)", "Antibiotics (-14 to -1)"),
                strata_level == "overall") |>
  dplyr::mutate(group_level = dplyr::case_when(
    group_level == "2551_ciprofloxacin" ~ "Ciprofloxacin",
    .default = group_level
  ),
  cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ))

CohortCharacteristics::tableCharacteristics(char, type = "flextable", header = c("cohort_name", "cdm_name"), hide = c("age_group_broad", "table_name", "value"))
```

## Table 3 - Vancomycin patient characteristics + indications

```{r char vanco, echo=FALSE, message = FALSE, warning = FALSE}
char_2 <- data[["summarise_characteristics"]] |>
  dplyr::filter(group_level == "11124_vancomycin",
                !variable_name %in% c("Antibiotics (-90 to -15)", "Antibiotics (-14 to -1)"),
                strata_level == "overall") |>
  dplyr::mutate(group_level = dplyr::case_when(
    group_level == "11124_vancomycin" ~ "Vancomycin",
    .default = group_level
  ),
  cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ))

CohortCharacteristics::tableCharacteristics(char_2, type = "flextable", header = c("cohort_name", "cdm_name"), hide = c("age_group_broad", "table_name", "value"))
```

## Figure 1 - Watch list outcome counts

```{r outcome counts, echo=FALSE, message = FALSE, warning = FALSE}
outcome_counts <- data[["incidence"]] |>
  dplyr::filter(estimate_name == "outcome_count") |>
  omopgenerics::splitAdditional() |>
  omopgenerics::splitGroup() |>
  omopgenerics::addSettings() |>
  dplyr::filter(denominator_age_group == "0 to 150",
                denominator_sex == "Both",
                analysis_interval == "overall") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    outcome_cohort_name = stringr::str_replace(outcome_cohort_name, "^\\d+_", ""),         # remove leading digits and underscore
    outcome_cohort_name = stringr::str_to_sentence(outcome_cohort_name), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  )

ggplot2::ggplot(outcome_counts, ggplot2::aes(x = outcome_cohort_name, y = estimate_value, fill = outcome_cohort_name)) +
  ggplot2::geom_bar(stat = "identity", colour = "black") +
  ggplot2::facet_wrap(~ cdm_name, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank()) 
```

## Figure 2 - Prior antibiotic use (-14 to -1) - Ciprofloxacin

```{r prior use, echo=FALSE, message = FALSE, warning = FALSE}
char_3 <- data[["summarise_characteristics"]] |>
  dplyr::filter(variable_name == "Antibiotics (-14 to -1)",
                strata_level == "overall") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    group_level = stringr::str_replace(group_level, "^\\d+_", ""),
    group_level = stringr::str_to_sentence(group_level), # capitalize first letter
    variable_level = stringr::str_replace(variable_level, "^\\d+ ", ""),         # remove leading digits and underscore
    variable_level = stringr::str_to_sentence(variable_level), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  ) |>
  dplyr::filter(estimate_name == "percentage",
                estimate_value >= 10)

ggplot2::ggplot(char_3, ggplot2::aes(x = variable_level, y = estimate_value, fill = variable_level)) +
  ggplot2::geom_bar(stat = "identity", colour = "black") +
  ggplot2::facet_wrap(~ cdm_name + group_level, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank())
```

## Figure 3 - Indications

```{r indications, echo=FALSE, message = FALSE, warning = FALSE}
char_4 <- data[["summarise_characteristics"]] |>
  dplyr::filter(variable_name == "Indication flag",
                strata_level == "overall") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    group_level = stringr::str_replace(group_level, "^\\d+_", ""),         # remove leading digits and underscore
    group_level = stringr::str_to_sentence(group_level), # capitalize first letter
    variable_level = stringr::str_replace(variable_level, "^\\d+ ", ""),         # remove leading digits and underscore
    variable_level = stringr::str_to_sentence(variable_level), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  ) |>
  dplyr::filter(estimate_name == "percentage",
                estimate_value >= 10)

ggplot2::ggplot(char_4, ggplot2::aes(x = group_level, y = estimate_value, fill = group_level)) +
  ggplot2::geom_bar(stat = "identity", colour = "black") +
  ggplot2::facet_wrap(~ cdm_name + variable_level, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank())
```

## Figure 4 - Incidence of Ciprofloxacin Use

```{r incidence, echo=FALSE, message = FALSE, warning = FALSE}
inc <- data[["incidence"]] |>
  dplyr::filter(estimate_name == "incidence_100000_pys") |>
  omopgenerics::splitAdditional() |>
  omopgenerics::splitGroup() |>
  omopgenerics::addSettings() |>
  dplyr::filter(denominator_age_group == "0 to 150",
                denominator_days_prior_observation == "0",
                denominator_sex == "Both",
                analysis_interval == "quarters") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    outcome_cohort_name = stringr::str_replace(outcome_cohort_name, "^\\d+_", ""),         # remove leading digits and underscore
    outcome_cohort_name = stringr::str_to_sentence(outcome_cohort_name), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  ) |>
  dplyr::filter(outcome_cohort_name == "Ciprofloxacin")

ggplot2::ggplot(inc, ggplot2::aes(x = incidence_start_date, y = estimate_value, colour = outcome_cohort_name, group = outcome_cohort_name)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~ cdm_name, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank()) 
```

## Figure 5 - Incidence of Vancomycin Use (Age + Sex)

```{r incidence 2, echo=FALSE, message = FALSE, warning = FALSE}
inc <- data[["incidence"]] |>
  dplyr::filter(estimate_name == "incidence_100000_pys") |>
  omopgenerics::splitAdditional() |>
  omopgenerics::splitGroup() |>
  omopgenerics::addSettings() |>
  dplyr::filter(denominator_age_group == "0 to 150",
                denominator_days_prior_observation == "0",
                analysis_interval == "quarters") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    outcome_cohort_name = stringr::str_replace(outcome_cohort_name, "^\\d+_", ""),         # remove leading digits and underscore
    outcome_cohort_name = stringr::str_to_sentence(outcome_cohort_name), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  ) |>
  dplyr::filter(outcome_cohort_name == "Vancomycin")

ggplot2::ggplot(inc, ggplot2::aes(x = incidence_start_date, y = estimate_value, colour = denominator_sex, group = denominator_sex)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~ cdm_name, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank()) 
```

```{r incidence 3, echo=FALSE, message = FALSE, warning = FALSE}
inc <- data[["incidence"]] |>
  dplyr::filter(estimate_name == "incidence_100000_pys") |>
  omopgenerics::splitAdditional() |>
  omopgenerics::splitGroup() |>
  omopgenerics::addSettings() |>
  dplyr::filter(denominator_age_group %in% c("0 to 150", "0 to 19", "20 to 64", "65 to 150"),
                denominator_sex == "Both",
                denominator_days_prior_observation == "0",
                analysis_interval == "quarters") |>
  dplyr::mutate(cdm_name = dplyr::case_when(
    cdm_name == "IDRIL_1" ~ "Lancashire",
    cdm_name == "LTHT" ~ "Leeds",
    .default = cdm_name
  ),
    outcome_cohort_name = stringr::str_replace(outcome_cohort_name, "^\\d+_", ""),         # remove leading digits and underscore
    outcome_cohort_name = stringr::str_to_sentence(outcome_cohort_name), # capitalize first letter
    estimate_value = as.numeric(estimate_value)
  ) |>
  dplyr::filter(outcome_cohort_name == "Vancomycin")

ggplot2::ggplot(inc, ggplot2::aes(x = incidence_start_date, y = estimate_value, colour = denominator_age_group, group = denominator_age_group)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::facet_wrap(~ cdm_name, scales = "free") +
  ggplot2::theme(axis.text.x = ggplot2::element_blank()) 
```
